Run aquaculture model for Atlantic salmon

### 2025-12-15 docs-working/07_run_atlantic_salmon_model.qmd
Re-order notebooks

```{r farm-coordinates}
#| code-summary: Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms

@@

```{r farm-sst-data}
#| label: farm-ts-data

@@

```{r species-parameters}
#| code-summary: Load species-specific parameters from Excel file

@@

```{r population-parameters}
#| code-summary: Load population-specific parameters

@@

```{r variable-digestibility}
#| code-summary: Show the variability in feed digestibility generated by sampling digestibility values.

@@

    data.frame(
      protein_digestibility = pd,
      carb_digestibility = cd,
      lipid_digestibility = ld,
      feed_name = fn
    )
  }) %>% 
  pivot_longer(
    cols = contains("digestibility"),
    names_to = "macro", 
    values_to = "digestibility"
  ) %>% 
  mutate(
    macro = factor(
      macro, 
      levels = c("protein_digestibility", "lipid_digestibility", "carb_digestibility"),
      labels = c("protein", "lipid", "carb")
    ))

feed_params %>% 
  ggplot(aes(x = macro, y = digestibility, fill = feed_name)) +
  geom_col(position = position_dodge(), alpha = 0.35) +
  theme_classic()
```

@@

Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline. This also allows you to run some tests and make sure the pipeline is running correctly.

@@

# tar_make(test_reference_feed)
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly
```

@@

tar_load(harvest_size_chunked)
harvest_size <- bind_rows(harvest_size_chunked)

@@

# tar_make(test_reference_feed)
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
```

```{r sensitivity-run, eval=F}
#| code-summary: Run sensitivity pipeline

@@

tar_make(seconds_meta_append = 300)
tar_prune()
```

@@

tar_load(stat_names)
tar_load(farm_IDs_chunked)
farm_IDs_chunked <- farm_IDs_chunked %>% unlist()
tar_load(feed_names)

print("Loading farm results...")
tar_load(farm_results_chunked)
farm_results_chunked <- farm_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  farm_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results_chunked)

print("Loading cohort results...")
tar_load(cohort_results_chunked)
cohort_results_chunked <- cohort_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  cohort_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
}
rm(cohort_results_chunked)

tar_load(biomass_produced_chunked)
qsave(biomass_produced_chunked, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
rm(biomass_produced_chunked)
```

>>>>

```{r farm-coordinates, eval=F}
#| code-summary: Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms

@@

```{r farm-sst-data, eval=F}
#| code-summary: Process Sea Surface Temperature (SST) data for each farm location.

@@

```{r species-parameters, eval=F}
#| code-summary: Load species-specific parameters from Excel file

@@

```{r population-parameters, eval=F}
#| code-summary: Load population-specific parameters

@@

```{r variable-digestibility}
#| code-summary: Show the variability in feed digestibility generated by sampling digestibility values.
#| fig-cap: Whole-feed digestibility of the feeds run in this analysis.

@@

    data.frame(
      protein_digestibility = pd,
      carb_digestibility = cd,
      lipid_digestibility = ld,
      feed_name = fn
    )
  }) %>% 
  pivot_longer(
    cols = contains("digestibility"),
    names_to = "macro", 
    values_to = "digestibility"
  ) %>% 
  mutate(
    macro = factor(
      macro, 
      levels = c("protein_digestibility", "lipid_digestibility", "carb_digestibility"),
      labels = c("protein", "lipid", "carb")
    ),
    feed_name = as.factor(feed_name)
  )

feed_params %>% 
  ggplot(aes(x = macro, y = digestibility, fill = feed_name)) +
  geom_col(position = position_dodge()) +
  theme_classic()
```

@@

First, let's test the pipeline to make sure that the feed input data is being processed correctly.

@@

# tar_make(test_reference_feed)
tar_load_globals()
reference_feed_name
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly
```

Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline. This sets a "target population" for each farm and grounds the growth somewhat.

@@

harvest_size <- tar_read(harvest_size_chunked) %>% 
  bind_rows()

@@

tar_make(test_reference_feed)
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
```

```{r sensitivity-run}
#| code-summary: Run sensitivity pipeline

@@

tar_make(contains("spec"), seconds_meta_append = 300)
tar_make(contains("pop"), shortcut = T, seconds_meta_append = 300)
tar_prune()
```

@@

Sys.setenv(TAR_PROJECT = "project_farmruns")
farm_IDs_chunked <- tar_read(farm_IDs_chunked) %>% unname() %>% unlist()
tar_load(feed_names)

tar_load(farm_full_results)
total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))
cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily"))

qsave(total_ends, file.path(output_model_farm_path, "total_ends.qs"))
qsave(cohort_results, file.path(output_model_cohort_path, "cohort_results.qs"))
rm(farm_full_results)
```
